Analyzing Fairness: Race, Recidivism, and the COMPAS Algorithm

### 2022-04-26 final_metrics_analysis.Rmd
adding plot titles

```{python mosiac of charge degrees by race}
props={}
props[('Caucasian','F')]={'facecolor': green, 'edgecolor':'white'}
props[('Caucasian','M')]={'facecolor':green, 'edgecolor':'white'}
props[('African-American','F')]={'facecolor':purple,'edgecolor':'white'}
props[('African-American','M')]=        {'facecolor':purple,'edgecolor':'white'}
labelizer=lambda k:{('Caucasian','F'):1242,('African-American','F'):2194,('Caucasian','M'):858,('African-American','M'):979}[k]
mosaic(df_viz,['race','c_charge_degree'],labelizer=labelizer,properties=props)
plt.show()
```

@@

```{python exploratory recidivism mosaic plot}
props={}
props[('Caucasian','Recidivated')]={'facecolor':green, 'edgecolor':'white'}
props[('Caucasian','Survived')]={'facecolor':green, 'edgecolor':'white'}
props[('African-American','Recidivated')]={'facecolor':purple,'edgecolor':'white'}
props[('African-American','Survived')]=        {'facecolor':purple,'edgecolor':'white'}
labelizer=lambda k:{('Caucasian','Recidivated'):822,('African-American','Recidivated'):1661,('Caucasian','Survived'):1278,('African-American','Survived'):1512}[k]
mosaic(df_viz,['race','two_year_recid'],labelizer=labelizer,properties=props)
plt.show()
```

@@

#plt.title("Prior Charges Count by Race and Sex)
plt.show()
```

>>>>

```{python mosiac of charge degrees by race}
props={}
props[('Caucasian','F')]={'facecolor': green, 'edgecolor':'white'}
props[('Caucasian','M')]={'facecolor':green, 'edgecolor':'white'}
props[('African-American','F')]={'facecolor':purple,'edgecolor':'white'}
props[('African-American','M')]={'facecolor':purple,'edgecolor':'white'}
labelizer=lambda k:{('Caucasian','F'):1242,('African-American','F'):2194,('Caucasian','M'):858,('African-American','M'):979}[k]
mosaic(df_viz,['race','c_charge_degree'],labelizer=labelizer,properties=props)

plt.title("Charge Degree by Race: Misdemeanors and Felonies")
plt.rcParams["figure.figsize"]=(7,7)
plt.show()
```

@@

```{python exploratory recidivism mosaic plot}
props={}
props[('Caucasian','Recidivated')]={'facecolor':green, 'edgecolor':'white'}
props[('Caucasian','Survived')]={'facecolor':green, 'edgecolor':'white'}
props[('African-American','Recidivated')]={'facecolor':purple,'edgecolor':'white'}
props[('African-American','Survived')]=        {'facecolor':purple,'edgecolor':'white'}
labelizer=lambda k:{('Caucasian','Recidivated'):822,('African-American','Recidivated'):1661,('Caucasian','Survived'):1278,('African-American','Survived'):1512}[k]
mosaic(df_viz,['race','two_year_recid'],labelizer=labelizer,properties=props)

plt.title("Recidivism Outcomes by Race")
plt.rcParams["figure.figsize"]=(7,7)
plt.show()
```

@@

plt.show()
```
